Meta-analysis of the Interoceptive Accuracy Scale

### 2025-01-06 analysis/study2.qmd
rendered correlation html + added data to correlations script

df1a <- cbind(data$df1a, scores$sample1a)
df1b <- cbind(data$df1b, scores$sample1b)
df2 <- cbind(data$df2, scores$sample2)
df3 <- cbind(data$df3, scores$sample3)
df4 <- cbind(data$df4, scores$sample4)
df5 <- cbind(data$df5, scores$sample5)
df6 <- cbind(data$df6, scores$sample6)
df7a <- cbind(data$df7a, scores$sample7a)
df7b <- cbind(data$df7b, scores$sample7b)
df7c <- cbind(data$df7c, scores$sample7c)
df8a <- cbind(data$df8a, scores$sample8a)
df8b <- cbind(data$df8b, scores$sample8b)
df9 <- cbind(data$df9, scores$sample9)
df10a <- cbind(data$df10a, scores$sample10a)
df10b <- cbind(data$df10b, scores$sample10b)

@@

# names(df1a)
# names(df1b)
# names(df2)  # BPQ, BVAQ, MAIA, ICQ (?), TAS
# names(df3)  # TAS, BPQ
# names(df4)  # BAQ (?), BPQ, MAIA, BRS (resilience?), PBCS (private bodily consciousness?)
# names(df5)  
# names(df6)  # IATS, SSS, GAD, PHQ2
# names(df7a)  # MAIA, STAI, FFMQ, NEOFFI, CES
# names(df7b)  # MAIA, STAI, BPQ, PHQ15, PHQ9
# names(df7c)  # TAS, BPQ, TAS, ASI, BDI, IASV
# names(df8a)  # EDI, BPQ
# names(df8b)  # TAS, PHQ15, PHQ9
# names(df9)  # BFI, STQ, EQ, ECR, 
# names(df10a)  # MAIA, PHQ4, PI, LIE, IPIP, PID, SPQ
# names(df10b)  # BDI, STAI, PHQ4
```

@@

vars_scores <- names(select(scores$sample1a, -Sample))
df_scores <- rbind(
  select(df1a, all_of(vars_scores)),
  select(df1b, all_of(vars_scores)),
  select(df2, all_of(vars_scores)),
  select(df3, all_of(vars_scores)),
  select(df4, all_of(vars_scores)),
  select(df5, all_of(vars_scores)),
  select(df6, all_of(vars_scores)),
  select(df7a, all_of(vars_scores)),
  select(df7b, all_of(vars_scores)),
  select(df7c, all_of(vars_scores)),
  select(df8a, all_of(vars_scores)),
  select(df8b, all_of(vars_scores)),
  select(df9, all_of(vars_scores)),
  select(df10a, all_of(vars_scores)),
  select(df10b, all_of(vars_scores))
)

@@

data <- rbind(
  make_diff(df1a, vars_intero, component="Demographic"),
  make_diff(df1b, vars_intero, component="Demographic"),
  make_diff(df2, vars_intero, component="Demographic"),
  make_diff(df3, vars_intero, component="Demographic"),
  # make_diff(df4, vars_intero, component="Demographic"),
  # make_diff(df5, vars_intero, component="Demographic"),
  make_diff(df6, vars_intero, component="Demographic"),
  make_diff(df7a, vars_intero, component="Demographic"),
  make_diff(df7b, vars_intero, component="Demographic"),
  make_diff(df7c, vars_intero, component="Demographic"),
  make_diff(df8a, vars_intero, component="Demographic"),
  make_diff(df8b, vars_intero, component="Demographic"),
  make_diff(df9, vars_intero, component="Demographic"),
  make_diff(df10a, vars_intero, component="Demographic"),
  make_diff(df10b, vars_intero, component="Demographic")
) |>
  mutate(var_Correlate = "Gender (Male vs. Female)")
```

@@

data <- rbind(
  data,
  make_cor(df1a, vars_intero, with = "Age", component="Demographic"),
  make_cor(df1b, vars_intero, with = "Age", component="Demographic"),
  make_cor(df2, vars_intero, with = "Age", component="Demographic"),
  make_cor(df3, vars_intero, with = "Age", component="Demographic"),
  # make_cor(df4, vars_intero, with = "Age", component="Demographic"),
  # make_cor(df5, vars_intero, with = "Age", component="Demographic"),
  make_cor(df6, vars_intero, with = "Age", component="Demographic"),
  make_cor(df7a, vars_intero, with = "Age", component="Demographic"),
  make_cor(df7b, vars_intero, with = "Age", component="Demographic"),
  make_cor(df7c, vars_intero, with = "Age", component="Demographic"),
  make_cor(df8a, vars_intero, with = "Age", component="Demographic"),
  make_cor(df8b, vars_intero, with = "Age", component="Demographic"),
  make_cor(df9, vars_intero, with = "Age", component="Demographic"),
  make_cor(df10a, vars_intero, with = "Age", component="Demographic"),
  make_cor(df10b, vars_intero, with = "Age", component="Demographic")
)
```

@@

```{r}
names(df2)[str_detect(names(df2), "MAIA")]  
names(df4)[str_detect(names(df4), "MAIA")]  # ?
names(df7a)[str_detect(names(df7a), "MAIA")]  
names(df7b)[str_detect(names(df7b), "maia")] 
names(df10a)[str_detect(names(df10b), "MAIA")]

@@

  # df10a
  make_cor(df10a, vars_intero, with = "MAIA_AttentionRegulation", component="MAIA")  |>
    mutate(var_Correlate = "Attention Regulation"),
  make_cor(df10a, vars_intero, with = "MAIA_BodyListening", component="MAIA") |>
    mutate(var_Correlate = "Listening"),
  make_cor(df10a, vars_intero, with = "MAIA_EmotionalAwareness", component="MAIA") |>
    mutate(var_Correlate = "Emotional Awareness"),
  make_cor(df10a, vars_intero, with = "MAIA_NotDistracting", component="MAIA") |>
    mutate(var_Correlate = "Not Distracting"),
  make_cor(df10a, vars_intero, with = "MAIA_Noticing", component="MAIA") |>
    mutate(var_Correlate = "Noticing"),
  make_cor(df10a, vars_intero, with = "MAIA_NotWorrying", component="MAIA") |>
    mutate(var_Correlate = "Not Worrying"),
  make_cor(df10a, vars_intero, with = "MAIA_SelfRegulation", component="MAIA") |>
    mutate(var_Correlate = "Self Regulation"),
  make_cor(df10a, vars_intero, with = "MAIA_Trusting", component="MAIA") |>
    mutate(var_Correlate = "Trusting")
)
```

@@

```{r}
names(df2)[str_detect(names(df2), "TAS")]
names(df3)[str_starts(names(df3), "TAS")]
names(df7c)[str_starts(names(df7c), "TAS")]
names(df8b)[str_starts(names(df8b), "TAS")]

data <- rbind(
  data,
  make_cor(df2, vars_intero, with = "TAS_DIF", component="Alexithymia") |>
    mutate(var_Correlate = "Difficulties Identifying Feelings (TAS)"),
  make_cor(df2, vars_intero, with = "TAS_DDF", component="Alexithymia") |>
    mutate(var_Correlate = "Difficulties Describing Feelings (TAS)"),
  make_cor(df2, vars_intero, with = "TAS_EOT", component="Alexithymia") |>
    mutate(var_Correlate = "External Thinking (TAS)"),
  make_cor(df3, vars_intero, with = "TAS_DescribingFeelings", component="Alexithymia") |>
    mutate(var_Correlate = "Difficulties Describing Feelings (TAS)"),
  make_cor(df3, vars_intero, with = "TAS_IdentifyingFeelings", component="Alexithymia") |> 
    mutate(var_Correlate = "Difficulties Identifying Feelings (TAS)"),
  make_cor(df3, vars_intero, with = "TAS_ExternallyOrientedThinking", component="Alexithymia") |>
    mutate(var_Correlate = "External Thinking (TAS)"),
  make_cor(df7c, vars_intero, with = "TAS_des", component="Alexithymia") |>
    mutate(var_Correlate = "Difficulties Describing Feelings (TAS)"),
  make_cor(df7c, vars_intero, with = "TAS_ident", component="Alexithymia") |>
    mutate(var_Correlate = "Difficulties Identifying Feelings (TAS)"),
  make_cor(df7c, vars_intero, with = "TAS_ext", component="Alexithymia") |>
    mutate(var_Correlate = "External Thinking (TAS)"),
  make_cor(df8b, vars_intero, with = "TAS_DIF", component="Alexithymia") |>
    mutate(var_Correlate = "Difficulties Identifying Feelings (TAS)"),
  make_cor(df8b, vars_intero, with = "TAS_DDF", component="Alexithymia") |>
    mutate(var_Correlate = "Difficulties Describing Feelings (TAS)"),
  # BVAQ
  make_cor(df2, vars_intero, with = "BVAQ_Affective", component="Alexithymia") |>
    mutate(var_Correlate = "Affective (BVAQ)"),
  make_cor(df2, vars_intero, with = "BVAQ_Cognitive", component="Alexithymia") |>
    mutate(var_Correlate = "Cognitive (BVAQ)")
)
```

@@

```{r}
names(df6)[str_detect(names(df6), "PHQ")] 
names(df7b)[str_detect(names(df7b), "PHQ")]
names(df7c)[str_detect(names(df7c), "BDI")]
names(df8b)[str_detect(names(df8b), "PHQ")]
names(df9)

data <- rbind(
  data,
  make_cor(df6, vars_intero, with = "PHQ2_sum", component="Mood") |>
    mutate(var_Correlate = "Depression (PHQ-2)"),
  make_cor(df7b, vars_intero, with = "PHQ15_Sum", component="Mood") |>
    mutate(var_Correlate = "Somatic Concerns (PHQ-15)"),
  make_cor(df7b, vars_intero, with = "PHQ9_Sum", component="Mood")|>
    mutate(var_Correlate = "Depression (PHQ-9)"),
  make_cor(df7c, vars_intero, with = "BDI_sum", component="Mood") |>
    mutate(var_Correlate = "Depression (BDI)"),
  make_cor(df8b, vars_intero, with = "PHQ15_sum", component="Mood") |>
    mutate(var_Correlate = "Somatic Concerns (PHQ-15)"),
  make_cor(df8b, vars_intero, with = "PHQ9_sum", component="Mood") |>
    mutate(var_Correlate = "Depression (PHQ-9)"),
  make_cor(df10a, vars_intero, with = "PHQ4_Depression", component="Mood") |>
    mutate(var_Correlate = "Depression (PHQ-2)"),
  make_cor(df10b, vars_intero, with = "BDI2_Total", component="Mood") |>
    mutate(var_Correlate = "Depression (BDI)")
)
```

@@

data <- rbind(
  data,
  make_cor(df6, vars_intero, with = "GAD2_sum", component="Mood") |>
    mutate(var_Correlate = "Anxiety (GAD-2)"),
  make_cor(df7a, vars_intero, with = "STAI_T_Sumscore", component="Mood") |>
    mutate(var_Correlate = "Anxiety (STAI)"),
  make_cor(df7b, vars_intero, with = "STAIT_Sum", component="Mood") |>
    mutate(var_Correlate = "Anxiety (STAI)"),
  make_cor(df7c, vars_intero, with = "STAIT_sum", component="Mood") |>
    mutate(var_Correlate = "Anxiety (STAI)"),
  make_cor(df10a, vars_intero, with = "PHQ4_Anxiety", component="Mood") |>
    mutate(var_Correlate = "Anxiety (GAD-2)"),
  make_cor(df10b, vars_intero, with = "PHQ4_Anxiety", component="Mood") |>
    mutate(var_Correlate = "Anxiety (GAD-2)"),
  make_cor(df10b, vars_intero, with = "STAI5_General", component="Mood") |>
    mutate(var_Correlate = "Anxiety (STAI)")
)
```

@@

```{r}
data <- rbind(
  data,
  make_cor(df10a, vars_intero, with = "PI_Alive", component="World Beliefs") |>
    mutate(var_Correlate = "Alive"),
  make_cor(df10a, vars_intero, with = "PI_Changing", component="World Beliefs") |>
    mutate(var_Correlate = "Changing"),
  make_cor(df10a, vars_intero, with = "PI_Enticing", component="World Beliefs") |>
    mutate(var_Correlate = "Enticing"),
  make_cor(df10a, vars_intero, with = "PI_Good", component="World Beliefs") |>
    mutate(var_Correlate = "Good"),
  make_cor(df10a, vars_intero, with = "PI_Hierarchical", component="World Beliefs") |>
    mutate(var_Correlate = "Hierarchical"),
  make_cor(df10a, vars_intero, with = "PI_Safe", component="World Beliefs") |>
    mutate(var_Correlate = "Safe"),
  make_cor(df10a, vars_intero, with = "PI_Understandable", component="World Beliefs") |>
    mutate(var_Correlate = "Understandable")
)
```

>>>>

df1a <- cbind(data$df1a, scores$sample1a)
df1b <- cbind(data$df1b, scores$sample1b)
df2 <- cbind(data$df2, scores$sample2)
df3 <- cbind(data$df3, scores$sample3)
df4 <- cbind(data$df4, scores$sample4)
df5 <- cbind(data$df5, scores$sample5)
df6 <- cbind(data$df6, scores$sample6)
df7a <- cbind(data$df7a, scores$sample7a)
df7b <- cbind(data$df7b, scores$sample7b)
df7c <- cbind(data$df7c, scores$sample7c)
df8a <- cbind(data$df8a, scores$sample8a)
df8b <- cbind(data$df8b, scores$sample8b)
df9 <- cbind(data$df9, scores$sample9)
df10a <- cbind(data$df10a, scores$sample10a)
df10b <- cbind(data$df10b, scores$sample10b)
df10c <- cbind(data$df10c, scores$sample10c)
df11a <- cbind(data$df11a, scores$sample11a)
df11b <- cbind(data$df11b, scores$sample11b)

@@

# names(df1a)
# names(df1b)
# names(df2)  # BPQ, BVAQ, MAIA, ICQ (?), TAS
# names(df3)  # TAS, BPQ
# names(df4)  # BAQ (?), BPQ, MAIA, BRS (resilience?), PBCS (private bodily consciousness?)
# names(df5)  
# names(df6)  # IATS, SSS, GAD, PHQ2
# names(df7a)  # MAIA, STAI, FFMQ, NEOFFI, CES
# names(df7b)  # MAIA, STAI, BPQ, PHQ15, PHQ9
# names(df7c)  # TAS, BPQ, TAS, ASI, BDI, IASV
# names(df8a)  # EDI, BPQ
# names(df8b)  # TAS, PHQ15, PHQ9
# names(df9)  # BFI, STQ, EQ, ECR, 
# names(df10a)  # MAIA, PHQ4, PI, LIE, IPIP, PID, SPQ
# names(df10b)  # BDI, STAI, PHQ4
# names(df10c) # PI, MAIA
# names(df11a) # MAIA, TAS, MFQ(DEP), STAI(ANX)
# names(df11b) 
```

@@

vars_scores <- names(select(scores$sample1a, -Sample))
df_scores <- rbind(
  select(df1a, all_of(vars_scores)),
  select(df1b, all_of(vars_scores)),
  select(df2, all_of(vars_scores)),
  select(df3, all_of(vars_scores)),
  select(df4, all_of(vars_scores)),
  select(df5, all_of(vars_scores)),
  select(df6, all_of(vars_scores)),
  select(df7a, all_of(vars_scores)),
  select(df7b, all_of(vars_scores)),
  select(df7c, all_of(vars_scores)),
  select(df8a, all_of(vars_scores)),
  select(df8b, all_of(vars_scores)),
  select(df9, all_of(vars_scores)),
  select(df10a, all_of(vars_scores)),
  select(df10b, all_of(vars_scores)),
  select(df10c, all_of(vars_scores)),
  select(df11a, all_of(vars_scores)),
  select(df11b, all_of(vars_scores))
)

@@

data <- rbind(
  make_diff(df1a, vars_intero, component="Demographic"),
  make_diff(df1b, vars_intero, component="Demographic"),
  make_diff(df2, vars_intero, component="Demographic"),
  make_diff(df3, vars_intero, component="Demographic"),
  #make_diff(df4, vars_intero, component="Demographic"),
  #make_diff(df5_attention, vars_intero, component="Demographic"),
  make_diff(df6, vars_intero, component="Demographic"),
  make_diff(df7a, vars_intero, component="Demographic"),
  make_diff(df7b, vars_intero, component="Demographic"),
  make_diff(df7c, vars_intero, component="Demographic"),
  make_diff(df8a, vars_intero, component="Demographic"),
  make_diff(df8b, vars_intero, component="Demographic"),
  make_diff(df9, vars_intero, component="Demographic"),
  make_diff(df10a, vars_intero, component="Demographic"),
  make_diff(df10b, vars_intero, component="Demographic"),
  make_diff(df10c, vars_intero, component="Demographic"),
  make_diff(df11a, vars_intero, component="Demographic"),
  make_diff(df11b, vars_intero, component="Demographic")
) |>
  mutate(var_Correlate = "Gender (Male vs. Female)")
```

@@

data <- rbind(
  data,
  make_cor(df1a, vars_intero, with = "Age", component="Demographic"),
  make_cor(df1b, vars_intero, with = "Age", component="Demographic"),
  make_cor(df2, vars_intero, with = "Age", component="Demographic"),
  make_cor(df3, vars_intero, with = "Age", component="Demographic"),
  # make_cor(df4, vars_intero, with = "Age", component="Demographic"),
  # make_cor(df5, vars_intero, with = "Age", component="Demographic"),
  make_cor(df6, vars_intero, with = "Age", component="Demographic"),
  make_cor(df7a, vars_intero, with = "Age", component="Demographic"),
  make_cor(df7b, vars_intero, with = "Age", component="Demographic"),
  make_cor(df7c, vars_intero, with = "Age", component="Demographic"),
  make_cor(df8a, vars_intero, with = "Age", component="Demographic"),
  make_cor(df8b, vars_intero, with = "Age", component="Demographic"),
  make_cor(df9, vars_intero, with = "Age", component="Demographic"),
  make_cor(df10a, vars_intero, with = "Age", component="Demographic"),
  make_cor(df10b, vars_intero, with = "Age", component="Demographic"),
  make_cor(df10c, vars_intero, with = "Age", component="Demographic"),
  make_cor(df11a, vars_intero, with = "Age", component="Demographic"),
  make_cor(df11b, vars_intero, with = "Age", component="Demographic")
)
```

@@

```{r}
names(df2)[str_detect(names(df2), "MAIA")]  
names(df4)[str_detect(names(df4), "MAIA")]  # ?
names(df7a)[str_detect(names(df7a), "MAIA")]  
names(df7b)[str_detect(names(df7b), "maia")] 
names(df10a)[str_detect(names(df10b), "MAIA")]
names(df10c)[str_detect(names(df10c), "MAIA")]
names(df11a)[str_detect(names(df11b), "MAIA")]

@@

  # df10a
  make_cor(df10a, vars_intero, with = "MAIA_AttentionRegulation", component="MAIA")  |>
    mutate(var_Correlate = "Attention Regulation"),
  make_cor(df10a, vars_intero, with = "MAIA_BodyListening", component="MAIA") |>
    mutate(var_Correlate = "Listening"),
  make_cor(df10a, vars_intero, with = "MAIA_EmotionalAwareness", component="MAIA") |>
    mutate(var_Correlate = "Emotional Awareness"),
  make_cor(df10a, vars_intero, with = "MAIA_NotDistracting", component="MAIA") |>
    mutate(var_Correlate = "Not Distracting"),
  make_cor(df10a, vars_intero, with = "MAIA_Noticing", component="MAIA") |>
    mutate(var_Correlate = "Noticing"),
  make_cor(df10a, vars_intero, with = "MAIA_NotWorrying", component="MAIA") |>
    mutate(var_Correlate = "Not Worrying"),
  make_cor(df10a, vars_intero, with = "MAIA_SelfRegulation", component="MAIA") |>
    mutate(var_Correlate = "Self Regulation"),
  make_cor(df10a, vars_intero, with = "MAIA_Trusting", component="MAIA") |>
    mutate(var_Correlate = "Trusting"),

  # df10c 
  make_cor(df10c, vars_intero, with = "MAIA_AttentionRegulation", component="MAIA")  |>
    mutate(var_Correlate = "Attention Regulation"),
  make_cor(df10c, vars_intero, with = "MAIA_BodyListening", component="MAIA") |>
    mutate(var_Correlate = "Listening"),
  make_cor(df10c, vars_intero, with = "MAIA_EmotionalAwareness", component="MAIA") |>
    mutate(var_Correlate = "Emotional Awareness"),
  make_cor(df10c, vars_intero, with = "MAIA_NotDistracting", component="MAIA") |>
    mutate(var_Correlate = "Not Distracting"),
  make_cor(df10c, vars_intero, with = "MAIA_Noticing", component="MAIA") |>
    mutate(var_Correlate = "Noticing"),
  make_cor(df10c, vars_intero, with = "MAIA_NotWorrying", component="MAIA") |>
    mutate(var_Correlate = "Not Worrying"),
  make_cor(df10c, vars_intero, with = "MAIA_SelfRegulation", component="MAIA") |>
    mutate(var_Correlate = "Self Regulation"),
  make_cor(df10c, vars_intero, with = "MAIA_Trusting", component="MAIA") |>
    mutate(var_Correlate = "Trusting"),

    # df11a
  make_cor(df11a, vars_intero, with = "MAIA_Attention", component="MAIA")  |>
    mutate(var_Correlate = "Attention Regulation"),
  make_cor(df11a, vars_intero, with = "MAIA_BodyListening", component="MAIA") |>
    mutate(var_Correlate = "Listening"),
  make_cor(df11a, vars_intero, with = "MAIA_Emotional", component="MAIA") |>
    mutate(var_Correlate = "Emotional Awareness"),
  make_cor(df11a, vars_intero, with = "MAIA_NotDistracting", component="MAIA") |>
    mutate(var_Correlate = "Not Distracting"),
  make_cor(df11a, vars_intero, with = "MAIA_Noticing", component="MAIA") |>
    mutate(var_Correlate = "Noticing"),
  make_cor(df11a, vars_intero, with = "MAIA_NotWorrying", component="MAIA") |>
    mutate(var_Correlate = "Not Worrying"),
  make_cor(df11a, vars_intero, with = "MAIA_SelfRegulation", component="MAIA") |>
    mutate(var_Correlate = "Self Regulation"),
  make_cor(df11a, vars_intero, with = "MAIA_Trusting", component="MAIA") |>
    mutate(var_Correlate = "Trusting")
)
```

@@

```{r}
names(df2)[str_detect(names(df2), "TAS")]
names(df3)[str_starts(names(df3), "TAS")]
names(df7c)[str_starts(names(df7c), "TAS")]
names(df8b)[str_starts(names(df8b), "TAS")]
names(df11a)[str_starts(names(df11a), "TAS")]

data <- rbind(
  data,
  make_cor(df2, vars_intero, with = "TAS_DIF", component="Alexithymia") |>
    mutate(var_Correlate = "Difficulties Identifying Feelings (TAS)"),
  make_cor(df2, vars_intero, with = "TAS_DDF", component="Alexithymia") |>
    mutate(var_Correlate = "Difficulties Describing Feelings (TAS)"),
  make_cor(df2, vars_intero, with = "TAS_EOT", component="Alexithymia") |>
    mutate(var_Correlate = "External Thinking (TAS)"),
  make_cor(df3, vars_intero, with = "TAS_DescribingFeelings", component="Alexithymia") |>
    mutate(var_Correlate = "Difficulties Describing Feelings (TAS)"),
  make_cor(df3, vars_intero, with = "TAS_IdentifyingFeelings", component="Alexithymia") |> 
    mutate(var_Correlate = "Difficulties Identifying Feelings (TAS)"),
  make_cor(df3, vars_intero, with = "TAS_ExternallyOrientedThinking", component="Alexithymia") |>
    mutate(var_Correlate = "External Thinking (TAS)"),
  make_cor(df7c, vars_intero, with = "TAS_des", component="Alexithymia") |>
    mutate(var_Correlate = "Difficulties Describing Feelings (TAS)"),
  make_cor(df7c, vars_intero, with = "TAS_ident", component="Alexithymia") |>
    mutate(var_Correlate = "Difficulties Identifying Feelings (TAS)"),
  make_cor(df7c, vars_intero, with = "TAS_ext", component="Alexithymia") |>
    mutate(var_Correlate = "External Thinking (TAS)"),
  make_cor(df8b, vars_intero, with = "TAS_DIF", component="Alexithymia") |>
    mutate(var_Correlate = "Difficulties Identifying Feelings (TAS)"),
  make_cor(df8b, vars_intero, with = "TAS_DDF", component="Alexithymia") |>
    mutate(var_Correlate = "Difficulties Describing Feelings (TAS)"),
  make_cor(df11a, vars_intero, with = "TAS_DIF", component="Alexithymia") |>
    mutate(var_Correlate = "Difficulties Identifying Feelings (TAS)"),
  make_cor(df11a, vars_intero, with = "TAS_DDF", component="Alexithymia") |>
    mutate(var_Correlate = "Difficulties Describing Feelings (TAS)"),
  make_cor(df11a, vars_intero, with = "TAS_EOT", component="Alexithymia") |>
    mutate(var_Correlate = "External Thinking (TAS)"),
  # BVAQ
  make_cor(df2, vars_intero, with = "BVAQ_Affective", component="Alexithymia") |>
    mutate(var_Correlate = "Affective (BVAQ)"),
  make_cor(df2, vars_intero, with = "BVAQ_Cognitive", component="Alexithymia") |>
    mutate(var_Correlate = "Cognitive (BVAQ)")
)
```

@@

```{r}
names(df6)[str_detect(names(df6), "PHQ")] 
names(df7b)[str_detect(names(df7b), "PHQ")]
names(df7c)[str_detect(names(df7c), "BDI")]
names(df8b)[str_detect(names(df8b), "PHQ")]
names(df9)
names(df11a)

data <- rbind(
  data,
  make_cor(df6, vars_intero, with = "PHQ2_sum", component="Mood") |>
    mutate(var_Correlate = "Depression (PHQ-2)"),
  make_cor(df7b, vars_intero, with = "PHQ15_Sum", component="Mood") |>
    mutate(var_Correlate = "Somatic Concerns (PHQ-15)"),
  make_cor(df7b, vars_intero, with = "PHQ9_Sum", component="Mood")|>
    mutate(var_Correlate = "Depression (PHQ-9)"),
  make_cor(df7c, vars_intero, with = "BDI_sum", component="Mood") |>
    mutate(var_Correlate = "Depression (BDI)"),
  make_cor(df8b, vars_intero, with = "PHQ15_sum", component="Mood") |>
    mutate(var_Correlate = "Somatic Concerns (PHQ-15)"),
  make_cor(df8b, vars_intero, with = "PHQ9_sum", component="Mood") |>
    mutate(var_Correlate = "Depression (PHQ-9)"),
  make_cor(df10a, vars_intero, with = "PHQ4_Depression", component="Mood") |>
    mutate(var_Correlate = "Depression (PHQ-2)"),
  make_cor(df10b, vars_intero, with = "BDI2_Total", component="Mood") |>
    mutate(var_Correlate = "Depression (BDI)"),
  make_cor(df11a, vars_intero, with = "DEP", component = "Mood") |>
    mutate(var_Correlate = "Depression (MFQ)")
)
```

@@

data <- rbind(
  data,
  make_cor(df6, vars_intero, with = "GAD2_sum", component="Mood") |>
    mutate(var_Correlate = "Anxiety (GAD-2)"),
  make_cor(df7a, vars_intero, with = "STAI_T_Sumscore", component="Mood") |>
    mutate(var_Correlate = "Anxiety (STAI)"),
  make_cor(df7b, vars_intero, with = "STAIT_Sum", component="Mood") |>
    mutate(var_Correlate = "Anxiety (STAI)"),
  make_cor(df7c, vars_intero, with = "STAIT_sum", component="Mood") |>
    mutate(var_Correlate = "Anxiety (STAI)"),
  make_cor(df10a, vars_intero, with = "PHQ4_Anxiety", component="Mood") |>
    mutate(var_Correlate = "Anxiety (GAD-2)"),
  make_cor(df10b, vars_intero, with = "PHQ4_Anxiety", component="Mood") |>
    mutate(var_Correlate = "Anxiety (GAD-2)"),
  make_cor(df10b, vars_intero, with = "STAI5_General", component="Mood") |>
    mutate(var_Correlate = "Anxiety (STAI)"),
  make_cor(df11a, vars_intero, with =  "ANX", component = "Mood") |>
    mutate(var_Correlate = "Anxiety (STAI)")
)
```

@@

```{r}
data <- rbind(
  data,
  make_cor(df10a, vars_intero, with = "PI_Alive", component="World Beliefs") |>
    mutate(var_Correlate = "Alive"),
  make_cor(df10a, vars_intero, with = "PI_Changing", component="World Beliefs") |>
    mutate(var_Correlate = "Changing"),
  make_cor(df10a, vars_intero, with = "PI_Enticing", component="World Beliefs") |>
    mutate(var_Correlate = "Enticing"),
  make_cor(df10a, vars_intero, with = "PI_Good", component="World Beliefs") |>
    mutate(var_Correlate = "Good"),
  make_cor(df10a, vars_intero, with = "PI_Hierarchical", component="World Beliefs") |>
    mutate(var_Correlate = "Hierarchical"),
  make_cor(df10a, vars_intero, with = "PI_Safe", component="World Beliefs") |>
    mutate(var_Correlate = "Safe"),
  make_cor(df10a, vars_intero, with = "PI_Understandable", component="World Beliefs") |>
    mutate(var_Correlate = "Understandable"),
  make_cor(df10c, vars_intero, with = "PI_Alive", component="World Beliefs") |>
    mutate(var_Correlate = "Alive"),
  make_cor(df10c, vars_intero, with = "PI_Changing", component="World Beliefs") |>
    mutate(var_Correlate = "Changing"),
  make_cor(df10c, vars_intero, with = "PI_Enticing", component="World Beliefs") |>
    mutate(var_Correlate = "Enticing"),
  make_cor(df10c, vars_intero, with = "PI_Good", component="World Beliefs") |>
    mutate(var_Correlate = "Good"),
  make_cor(df10c, vars_intero, with = "PI_Hierarchical", component="World Beliefs") |>
    mutate(var_Correlate = "Hierarchical"),
  make_cor(df10c, vars_intero, with = "PI_Safe", component="World Beliefs") |>
    mutate(var_Correlate = "Safe"),
  make_cor(df10c, vars_intero, with = "PI_Understandable", component="World Beliefs") |>
    mutate(var_Correlate = "Understandable")
)
```
